HTW Project

### 2024-04-02 Sections/HTW_old.qmd
update htw page

---
title: HTW Project
date: last-modified
page-layout: full
bibliography: "Assets/Bib/Dissertation.bib"
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-title: Contents
execute: 
  warning: false
  eval: true
---

@@

{{< include Sections/htw_exam.qmd >}}

>>>>

---
title: HTW Project
date: last-modified
page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-title: Contents
execute: 
  warning: false
  eval: true
---

@@

{{< include htw_exam.qmd >}}
